---
title: "Task 3"
author: "Jiaqing"
date: "3/4/2019"
output:
  word_document: default
  html_document: default
---


```{r}
wages<-readRDS("/Users/jiaqingzhang/Downloads/wages.rds")
names(wages)
dim(wages)
```

### 1.1 Generative Model

For the  endogenous known variable (WAGP), I think wage variable should be normally distributed as less people with extremely high or low income. The mean is $\mu$ and standard deviation is $\sigma$.
$\beta_1$, which is the coefficient for the age variable (AGEP), is normally distributed as well. 
$\beta_2$, which is the coefficeint for the gender, is normally distributed.
$\beta_3$, which is the coefficent for hours worked per week, follows a normal distribution.
$\beta_4$, which is the coefficent for educational attainment, is following a normal distribution.


###1.2 Prior Median of R^2
The $R^2$ in the previous model is the variance of wage explained by the predictors (age, insurance coverage, public assitance, gender, hours worked per week, and educational attainment). The median of $R^2$ may be 50%. 

###1.3 Prior Predictive Distribution
The median of the prior predictive $R^2$ using the ratio of the varaince of the conditional mean to the variance of the predictive mean is about 68%, which is much larger than we specified in the previous question. Moreover, not all $R^2$ are bounded to (0, 1).
However, if different formulas of $R^2$ are used, as suggested in the paper http://www.stat.columbia.edu/~gelman/research/unpublished/bayes_R2.pdf, we will get $R^2$ about 50%. It is very close to that which we asserted in the previous question. 
```{r, message = FALSE, warning=FALSE}
##prior predictive distribution
library(rstanarm)
##do some transformation to recenter the predictors:
wages$age.1<-wages$AGEP#-mean(wages$AGEP)
wages$sex.1<-as.integer(wages$SEX)-1L
wages$WKHP.1<-wages$WKHP#-mean(wages$WKHP)
wages$SCHL.1<-as.integer(wages$SCHL)#-mean(wages$SCHL)

prior<-stan_glm(log(PWGTP)~age.1+sex.1+WKHP.1+SCHL.1, data=wages, family = gaussian, prior_PD=TRUE, iter=1000, prior_intercept = normal(location = 0, scale = 30, autoscale = FALSE), prior=normal(location = 0, scale = 30,  autoscale = FALSE), prior_aux = cauchy(0, 30, autoscale = FALSE), QR=FALSE)

prior

##predictive distribution
predi_out<-posterior_predict(prior, draws=250)
dim(predi_out)

##conditional mean
predi_linpred<-posterior_linpred(prior, transform=TRUE, draws=250)
dim(predi_linpred)

e<--1*sweep(predi_linpred, 2, get_y(prior)) ##
var_e<-apply(e, 1, var)

pred.var<-apply(predi_out, MARGIN = 1, FUN = var)
length(pred.var)
condi.var<-apply(predi_linpred, MARGIN = 1, FUN = var)
length(condi.var)

##R^2
r_2.1<-condi.var/pred.var
median(r_2.1[which(r_2.1<1 & r_2.1>0)])
hist(r_2.1[which(r_2.1<1)], breaks = 10)


r_2.2<-condi.var/(condi.var+var_e)
median(r_2.2)
hist(r_2.2)

median(bayes_R2(prior, newdata = NULL, draws=250))
hist(bayes_R2(prior, newdata = NULL, draws=250))
```



